The Heavy Photon Search Test Detector

### 2013-11-15 hps-testrun-nim.tex
Removed brand name of router to be consistent.

\subsection{Data Acquisition and Online Computing}
\label{sec:daq}
For the ECal, every VXS crate contains a Readout Controller (ROC)
that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a 
single blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT 
ATCA system, the ROC application runs on an embedded processor situated on the ATCA main board. 
The EB assembles information from the SVT and ECal ROCs into a single event which is passed to the 
Event Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 
100~MB/s. The EB and other critical components run on multicore Intel-based multi-CPU servers. The 
DAQ network system is a Foundry router providing high-speed connections between the DAQ 
components and the JLab computing facility. The SVT ROC, which must handle large data volumes, has 
a 10~Gbit/s link to the Foundry router, while a 1~Gbit/s link is adequate for the ECal. A 10~Gbit/s uplink 
to the JLab computing facility is used for long-term storage.

>>>>

\subsection{Data Acquisition and Online Computing}
\label{sec:daq}
For the ECal, every VXS crate contains a Readout Controller (ROC)
that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a 
single blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT 
ATCA system, the ROC application runs on an embedded processor situated on the ATCA main board. 
The EB assembles information from the SVT and ECal ROCs into a single event which is passed to the 
Event Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 
100~MB/s. The EB and other critical components run on multicore Intel-based multi-CPU servers. The 
DAQ network system is a network router providing high-speed connections between the DAQ 
components and the JLab computing facility. The SVT ROC, which must handle large data volumes, has 
a 10~Gbit/s link to the network router, while a 1~Gbit/s link is adequate for the ECal. A 10~Gbit/s uplink 
to the JLab computing facility is used for long-term storage.
